Fourmile

### 2024-07-16 fourmile_dataprocess.Rmd
reminders

#look at 2011-2013
hydro_datelimit <- ggplot(daily_q, aes(x=date, y=q_m3s, color=site)) + geom_line() + 
  theme_bw() + 
  scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
  ylim(0,4) +
  ggtitle('Daily streamflow (2011-2013)')

>>>>

#look at 2011-2013
hydro_datelimit <- ggplot(daily_q_ds3, aes(x=date, y=q_m3s, color=site)) + geom_point() + 
  theme_bw() + 
  scale_x_date(limits = as.Date(c('2011-01-01', '2014-01-01'))) +
  ylim(0,4) +
  ggtitle('Daily streamflow (2011-2013)')
